### 2005-11-22 Documentation/tutorials/norm.tex
PH -- changed the author

\vspace*{-3.cm}
\begin{flushright}
\today
%TUM-HEP-553/04\\
%hep-ph/
\end{flushright}

@@

\vspace*{.8cm}
%\vspace*{.3cm}
{\begin{center} {\large{\sc
                P.~Huber\footnote[1]{\makebox[1.cm]{Email:}
                phuber@physics.wisc.edu}
             %   M.~Lindner\footnote[2]{\makebox[1.cm]{Email:}
             %   lindner@ph.tum.de},~and~
             %   W.~Winter\footnote[3]{\makebox[1.cm]{Email:}
             %   wwinter@ph.tum.de}
                }}
\end{center}}
\vspace*{0cm}
{\it
\begin{center}

\footnotemark[1]${}^,$% 
      Department of Physics, University of Wisconsin,\\ 
 1150 University
      Avenue, Madison ,WI 53706, USA

@@

\GLOBES\ assume that the cross
section $x$ is given in $10^{-38}\,\mathrm{cm}^2$, that all fluxes are
given at a distance of $1\,\mathrm{km}$ and the proper accounting for
the number of target nuclei $\tau$ (or protons or whatever applies to the
given cross section) per unit target mass $m_u$ (which usually is {\it
  kt}), is dealt with in the
definition of the flux inside \AEDL.  Assuming that in the flux file
the data is given as number of neutrinos per unit area $A$ and
energy bin of width $\Delta E$ at a distance $L$ from the source, one
obtains

\begin{eqnarray}
(\mathtt{@norm})^{-1}=5.20034\left(\frac{\Delta E}{\mathrm{GeV}}\right)\left(\frac{A}{\mathrm{cm}^2}\right)\left(\frac{\mathrm{km}}{L}\right)^2\left(\frac{\tau}{m_u}\right)\times10^{-38}\times\left(\frac{\mathcal{L}}{\mathcal{L}_u}\right)
\end{eqnarray}
where the $\mathcal{L}$ absorbs all factors in the flux file related to
the integrated luminosity and $\mathcal{L_u}$ is the unit chosen for
it.  The concept of integrated luminosity is
nicely described in the \GLOBES\ manual:

>>>>

\vspace*{-3.cm}
\begin{flushright}
\today\\
GLoBES-FAQ-1/05
%TUM-HEP-553/04\\
%hep-ph/
\end{flushright}

@@

\vspace*{.8cm}
%\vspace*{.3cm}
{\begin{center} {\large{\sc
                The \GLOBES\ Team\footnote[1]{\makebox[1.cm]{Email:}
                globes@ph.tum.de}
             %   M.~Lindner\footnote[2]{\makebox[1.cm]{Email:}
             %   lindner@ph.tum.de},~and~
             %   W.~Winter\footnote[3]{\makebox[1.cm]{Email:}
             %   wwinter@ph.tum.de}
                }}
\end{center}}
\vspace*{0cm}
{\it
\begin{center}

@@

\GLOBES\ assumes that the cross
section $x$ is given in $10^{-38}\,\mathrm{cm}^2$, that all fluxes are
given at a distance of $1\,\mathrm{km}$ and the proper accounting for
the number of target nuclei $\tau$ (or protons or whatever applies to the
given cross section) per unit target mass $m_u$ (which usually is {\it
  kt}), is dealt with in the
definition of the flux inside \AEDL.  Assuming that in the flux file
the data is given as number of neutrinos per unit area $A$ and
energy bin of width $\Delta E$ at a distance $L$ from the source, one
obtains

\begin{eqnarray}
(\mathtt{@norm})^{-1}=5.20034\left(\frac{\Delta E}{\mathrm{GeV}}\right)\left(\frac{A}{\mathrm{cm}^2}\right)\left(\frac{\mathrm{km}}{L}\right)^2\left(\frac{\tau}{m_u}\right)\times10^{-38}\times\left(\frac{\mathcal{L}}{\mathcal{L}_u}\right)
\end{eqnarray}
where the $\mathcal{L}$ absorbs all factors in the flux file related to
the integrated luminosity and $\mathcal{L}_u$ is the unit chosen for
it.  The concept of integrated luminosity is
nicely described in the \GLOBES\ manual:
